\documentclass[11pt, a4paper]{article}

\usepackage{amsmath}
\usepackage{commath}
\usepackage{url}
\usepackage{cite}
\usepackage{color}
\usepackage{multirow}
\usepackage[margin=1.25in]{geometry}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\graphicspath{{./graphics/}}

\usepackage{subfiles}
\usepackage{blindtext}

\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut

\newcommand{\gluex}{{\sc GlueX}\xspace}
\newcommand{\geant}{{\sc Geant}\xspace}
\newcommand{\babar}{BaBar\xspace}
\newcommand{\mydeg}{$^{\circ}$\xspace}
\newcommand{\myfar}{$^{\circ}$F\xspace}
\newcommand{\mycel}{$^{\circ}$C\xspace}
\newcommand{\eqdeg}{^{\circ}\xspace}
\newcommand{\deltall}{$\Delta$LL\xspace}
\newcommand{\bboson}{\emph{B} boson\xspace}
\newcommand{\bbosons}{\emph{B} bosons\xspace}
\newcommand{\gev}{~GeV\xspace}
\newcommand{\mev}{~MeV\xspace}

\title{GlueX DIRC Writeup}

\author[1]{M.~Patsyuk\thanks{mpatsyuk@mit.edu}}
\author[2]{R.~Dzhydaglo\thanks{r.dzhygadlo@gsi.de}}
\author[1]{J.~M.~Hardin\thanks{jmhardin@mit.edu}}
\affil[1]{\small{Massachusetts Institute of Technology, Cambridge, USA}}
\affil[2]{\small{GSI Helmholtzzentrum f{\"u}r Schwerionenforschung GmbH, Darmstadt, Germany}}

\date{\vspace{-5ex}}

\begin{document}

\maketitle

\input{abstract.tex}

\vspace{8cm}
\begin{center}
Version 2.0
\end{center}

\newpage

\tableofcontents

\newpage

\input{detectorDesign.tex}

\section{Simulation}
%\label{sec:sim}

A detailed physical simulation of was developed using Geant4 (\texttt{hdgeant4} package of the GlueX software). This chapter describes the details of the detector simulation, including the geometry, materials, and physical processes relevant for Cherenkov photons propagation. 

\input{geometry.tex}

\input{physProc.tex}

\input{materials.tex}

\input{signal.tex}

\section{Reconstruction}

Three reconstruction approaches are being implemented into the GlueX Software. The geometrical reconstruction is fully implemented and can be used at the beginning of the DIRC operation. The time-based imaging  needs some development effort. The KDE-based reconstruction was very useful for the design work. This method is to be implemented into the software.

\input{geometrical}

%\input{loglikelihoods}

\input{ti}

\input{kde}

%\subsection{Comparison of Performance}

\newpage

\begin{thebibliography}{1}
\bibitem{dirc} F.~Barbosa et al., ``The GlueX DIRC detector'', NIM \textbf{A} 876 (2017) 69.
\bibitem{gluex1} GlueX Collaboration, ``Mapping the Spectrum of Light Quark Mesons and Gluonic Excitations with Linearly Polarized Photons'', Jefferson Lab PAC 30 Proposal, 2006.
\bibitem{gluex2} A.~AlekSejevs et al., GlueX Collaboration, \url{arXiv:1305.1523}.
\bibitem{gluex3} M.~Dugger et al., GlueX Collaboration, \url{arXiv:1408.0215}. 
\bibitem{bdirc1} I.~ Adam et al., NIM \textbf{A} 538 (2005) 235.
\bibitem{fdirc} B.~Dey et al., NIM \textbf{A} 775 (2015) 112.
\bibitem{scalar} H.~Bennet, J.~Elson, and J.~Bennet ``Scattering from optical surfaces'' Vol. 7. Applied Optics and Optical Engineering. Academic Press New York, 1979.
\bibitem{roughness} J.~Cohen-Tanugi et al., ``Optical properties of the DIRC fused silica Cherenkov radiator'', NIM \textbf{A} 515 (2003) 680. 
\bibitem{Epotek} Epoxy Technology, Inc. 14 Fortune Drive Billerica, MA 01821.
\bibitem{EpotekData} BABAR DIRC Note 140 ``Measurement of Epotek-301-2 Optical Glue Refraction Index and Reflectivity from Epotek-301-2/Fused Silica Interface'', J. Va'vra (2001).
\bibitem{pcpaper} D.~Motta, S.~Sch{\"o}nert ``Optical properties of bialkali photocathodes'' NIM \textbf{A} 539 (2005) 217. 
\bibitem{water} A.~Morel ``Optical properties of Pure Water and Pure Sea Water'', Academic Press, 1974.
\bibitem{water2} R.~R{\"o}ttgers, ``Measurements of inherent optical properties of pure water'', Technical note, GKSS Forschungszentrum in der Helmholtz Gemeindschaft.
\bibitem{tdr} GlueX Collaboration, ``GlueX DIRC Technical Design Report'', 2015.
\bibitem{staric2} M.~Staric et al., ``Pattern recognition for the time-of-propagation counter'', NIM \textbf{A} 639 (2011) 252.
\bibitem{staric3} M.~Static et al., ``Likelihood analysis of patterns in a time-of-propagation (TOP) counter'', NIM \textbf{A} 595 (2008) 252.
\bibitem{Hardin:2016cvu} J.~Hardin and M.~Williams, ``FastDIRC: a fast Monte Carlo and reconstruction algorithm for DIRC detectors'', JINST 11 (2016).
\bibitem{hardinGithub}\url{https://github.mit.edu/jmhardin/FastDIRC}.
\bibitem{hardinWebDists}\url{www.mit.edu/~jmhardin/worklinks/dirc\_distros.html}.

\end{thebibliography}


\end{document}
